---
title: "A primer on zz_lite"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-primer-on-zz_lite}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `zz_lite` package is a collection of functions that simplifies communication between R and the [Zamzar Online file conversion](https://developers.zamzar.com/user) API.  

By utilizing `zz_lite` (and thereby the Zamzar API) you can easily convert between [hundreds](https://developers.zamzar.com/formats) of file formats from R.

## The basics

The following section serves as a simple introduction to get you started with the `zz_lite` package. It is assumed that you already have a valid (and nonexhausted) Zamzar API key at your disposal. If not, go signup via [Zamzar](https://developers.zamzar.com/)s website. Otherwise, keep on reading.  


### On Zamzar API keys in `zz_lite`

There's two ways in which you can pass a Zamzar key to `zz_lite`.  

1. By passing a hardcoded Zamzar key as an argument to the `usr` parameter. The `usr` parameter is available in all functions that are communication with Zamzars webservice.  

2. By leveraging an `.Renviron` file. Simply create a variable called `ZAMZAR_USR` in your `.Renviron` and pass it your Zamzar key. If done succesfully, you can skip passing a key to `usr` param whenever you're invoking a `zz_lite` function.  


<center>_Example of .Renviron:_</center>
```sh
## Zamzar key used by zz_lite 
ZAMZAR_USR=77c39dh6lo03g7598t98h659ihg99b7ny7213q




```



### `zz_format()`



### `zz_post()`

### `zz_get_info()`

### `zz_get()`

```{r setup}
library(zzlite)
```

